Maximizing Council Participation: A Study on Toronto City Council Absences (2022-2026)

### 2024-09-27 paper/paper.qmd
page styling changes
fixing lintr style

# Filter the data to only include rows where members were absent (present == "No")
absent_data <- cleaned_data %>%
  filter(present == "No") %>%
  group_by(session_year) %>%
  summarise(absence_count = n())  # Count the number of absences by year

# Create the plot
ggplot(absent_data, aes(x = session_year, y = absence_count)) +
  geom_bar(stat = "identity", fill = "cyan3") +  # Use a bar plot and custom color
  labs(
    title = "Number of Absence Over Years 2022-2024",
    x = "Year",
    y = "Number of Absences"
  ) +
  theme_minimal()
```

@@

# Filter the data for absences (present == "No") and group by session type
absence_data <- cleaned_data %>%
  filter(present == "No") %>%
  group_by(session_type) %>%
  summarise(absence_count = n())  # Count the number of absences for each session type

# Create the plot
ggplot(absence_data, aes(x = session_type, y = absence_count)) +
  geom_bar(stat = "identity", fill = "cyan3") +  # Use horizontal bar plot and a custom color
  labs(
    title = "Number Absence for Different Meetings Types",
    x = "Session Type",
    y = "Number of Absences"
  ) +
  theme_minimal()
```

>>>>

# Filter data to only include rows where members were absent (present == "No")
absent_data <- cleaned_data %>%
  filter(present == "No") %>%
  group_by(session_year) %>%
  summarise(absence_count = n())  # Count the number of absences by year

# Create the plot
ggplot(absent_data, aes(x = session_year, y = absence_count)) +
  # Use a bar plot and custom color
  geom_bar(stat = "identity", fill = "cyan3") +
  labs(
    title = "Number of Absence Over Years 2022-2024",
    x = "Year",
    y = "Number of Absences"
  ) +
  theme_minimal()
```

@@

# Filter the data for absences (present == "No") and group by session type
absence_data <- cleaned_data %>%
  filter(present == "No") %>%
  group_by(session_type) %>%
  # Count the number of absences for each session type
  summarise(absence_count = n())

# Create the plot
ggplot(absence_data, aes(x = session_type, y = absence_count)) +
  # Use horizontal bar plot and a custom color
  geom_bar(stat = "identity", fill = "cyan3") +
  labs(
    title = "Number Absence for Different Meetings Types",
    x = "Session Type",
    y = "Number of Absences"
  ) +
  theme_minimal()
```
